---
title: "Benchmark exercise"
author: "Abby Lewis"
date: "2023-08-11"
output: html_document
---

# Warm-up exercise

Working individually, brainstorm two ways to calculate the mean of each column of this example data frame. Try to use a for loop for at least one of your options.

```{r test-matrix}
set.seed(47)
m <- data.frame(matrix(runif(1E5, max = 100), ncol = 100))



```

As a class, implement several options as functions. Make predictions as to which options will be fastest and why

```{r}
#f1 <- function(m) {}
#f2 <- function(m) {}
#f3 <- function(m) {}
```

Check if outputs are the same with all approaches

```{r}
identical(f1(m),
          f2(m),
          f3(m))
```


Use the `microbenchmark` package to compare the speed of these options

```{r}
library(microbenchmark)
compare <- microbenchmark(f1(m), 
                          f2(m), 
                          f3(m),
                          times = 100
                          )

ggplot2::autoplot(compare)
```

## Discussion questions

* What factors make these approaches more and less efficient? 
* Do you expect the same patterns with larger datasets? Smaller datasets?
* In your own work, have there been times where code efficiency was a concern? If so, what have you done to address this concern?
* Aside from efficiency, what factors may make some of these options better than others?
